Analysing the Fish Hunting Numbers in North Pacific Ocean

### 2024-11-27 paper/paper.qmd
fixed the latex issue where model summary wont show up "Just installed the tinytax stuff on qerto page"

---
title: "Analysing the Fish Hunting Numbers in North Pacific Ocean"
subtitle: "Using Baysian Modeling, to find that number of fish caught has increased"
author: "Shreya Sakura Noskor"
thanks: "Code and data are available at: [https://github.com/NotSakura/FisheriesData.git](https://github.com/NotSakura/FisheriesData.git)."
date: today
date-format: long
abstract: "We analyzed data on fish catches in the North Pacific Ocean using Bayesian modeling. Our analysis shows that the number of fish caught has increased over time. This suggests that fishing activities in the region have intensified. Understanding this trend is important for managing fish populations and ensuring the sustainability of the ocean's resources. This is important as the Pacific is full of different kind of fish like, trout and salmon that are essential in the food chain, but are being overhunted for food and recreational purposes."
format:
  pdf:
    bibliography: references.bib
    documentclass: article
    geometry: margin = 1in
number-sections: true
toc: true
bibliography: references.bib
---

@@

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig_model1
#| tbl-cap: "baysian model summary for predicting the rate of fishes being caught"

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig_model2
#| tbl-cap: "baysian model summary for predicting the probability of country fishing for commercial purposes."
modelsummary::modelsummary(
  list(
    "Second model" = bayesian_model_commercial_brms
  ),
  statistic = "mad",
  fmt = 2
)
```

>>>>

---
title: "Analysing the Fish Hunting Numbers in North Pacific Ocean"
subtitle: "Using Baysian Modeling, to find that number of fish caught has increased"
author: "Shreya Sakura Noskor"
thanks: "Code and data are available at: [https://github.com/NotSakura/FisheriesData.git](https://github.com/NotSakura/FisheriesData.git)."
date: today
date-format: long
abstract: "We analyzed data on fish catches in the North Pacific Ocean using Bayesian modeling. Our analysis shows that the number of fish caught has increased over time. This suggests that fishing activities in the region have intensified. Understanding this trend is important for managing fish populations and ensuring the sustainability of the ocean's resources. This is important as the Pacific is full of different kind of fish like, trout and salmon that are essential in the food chain, but are being overhunted for food and recreational purposes."
format:
  pdf:
    bibliography: references.bib
    documentclass: article
    geometry: margin = 1in
header-includes:
  - \usepackage{float} 
  - \floatplacement{table}{H}
number-sections: true
include-in-header: 
  text:
    \renewcommand{\abstractname}{Abstract}
bibliography: references.bib
toc: true
---

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. We also use `brm` package from @brms

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-model1
#| tbl-cap: "baysian model summary for predicting the rate of fishes being caught"

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-model2
#| tbl-cap: "baysian model summary for predicting the probability of country fishing for commercial purposes."

modelsummary::modelsummary(
  list(
    "Second model" = bayesian_model_commercial_brms
  ),
  statistic = "mad",
  fmt = 2
)
```
